\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{mathptmx}
% \usepackage{palatino}
\usepackage{changepage}

\newenvironment{absolutelynopagebreak}
  {\par\nobreak\vfil\penalty0\vfilneg
   \vtop\bgroup}
  {\par\xdef\tpd{\the\prevdepth}\egroup
   \prevdepth=\tpd}

\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%\lfoot{\footnotesize Brook Luers}
%\rfoot{\footnotesize Page~\thepage~of~\pageref{sec:lastpage}}
\cfoot{\footnotesize Brook Luers---Page~\thepage~of~\pageref{sec:lastpage}}

% Adjust margins
\addtolength{\oddsidemargin}{-.25in}
\addtolength{\evensidemargin}{-.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.55in}
%\addtolength{\textheight}{0.5in}


\urlstyle{same}

\setlength{\tabcolsep}{0in}
\setlength{\headheight}{36pt}
\setlength{\headsep}{6pt}
\setlength{\parskip}{6pt}
\setlength{\footskip}{18pt}

\setlist{topsep=0pt, itemsep=0pt, parsep=0pt}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\raggedbottom
\raggedright
\pagestyle{fancy}
%\addtolength{\headwidth}{\marginparsep}
%\addtolength{\headwidth}{\marginparwidth}

\fancypagestyle{plain}
\fancyhf{}
\begin{document} 
\thispagestyle{plain}


\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://brookluers.com/}{\Large Brook Luers}} & Department of Statistics\\ 
  \href{http://brookluers.com/}{http://www.brookluers.com} &  311 West Hall\\ 
\href{mailto:luers@umich.edu}{luers@umich.edu}   &  1085 South University\\
 &  Ann Arbor, MI 48109
\end{tabular*}

\vspace{18pt}
\section{EDUCATION}          

{\bf Ph.D.}, Statistics (expected 2020) \\
University of Michigan, Ann Arbor, MI\\
%Passed qualifying exams, May 2016\\

\vspace{6pt}
{\bf M.S.}, Statistics, May 2015\\
University of Wisconsin-Madison, Madison, WI\\
GPA: 3.78 out of 4.0

\vspace{6pt}
{\bf B.A.}, Mathematics, May 2012\\
Oberlin College, Oberlin, OH\\
GPA: 3.81 out of 4.0

%\section{SELECTED COURSEWORK}
% \section{GRADUATE COURSEWORK}
% %\vspace{6pt}
% %\textbf{Graduate} &\textbf{Undergraduate}\\
% %Statistical consulting  & Multivariable calculus\\
% %Theory and application of regression and analysis of variance I and II
% %& Foundations of analysis (Mathematics)\\
% %Biostatistical modeling with generalized linear models & Linear algebra\\
% %Mathematical statistics& Group theory\\
% %Introduction to statistical inference & Systems programming
%  Statistical consulting\\[6pt]
%  Theory and application of regression and analysis of variance I and II\\[6pt]
%  Biostatistical modeling with generalized linear models\\[6pt]
%  Statistical methods for clinical trials\\[6pt]
%  Mathematical statistics\\[6pt]
%  Introduction to statistical inference 

\section{PROFESSIONAL/RESEARCH EXPERIENCE}

{\bf University of Michigan}, Ann Arbor, MI\\
Graduate Research Assistant \hfill Summer 2016--present

{\addtolength{\leftskip}{15pt}\textit{Longitudinal SMARTs (with Daniel Almirall, Ph.D.)}\\% \hfill January 2018--present\\
%\textit{Advisor: Daniel Almirall, Ph.D.}\\
Methodology for mixed effects modeling of data from sequential, multiple assignment randomized trials (SMARTs) with longitudinal outcomes. %\href{http://d3lab-isr.com/}{http://d3lab-isr.com/}.

}

{\addtolength{\leftskip}{15pt}\textit{Variable selection with large-scale observational data (with Kerby Shedden, Ph.D.)}\\% \hfill Spring 2017--present\\
%\textit{Advisor: Kerby Shedden, Ph.D.}\\
Extended the ``knockoff'' variable selection technique to improve power with correlated features.
Performed case studies of knockoff variable selection with large-scale insurance claims and U.S. Census data.

}

{\addtolength{\leftskip}{15pt} \textit{Sequential decision making in mobile health (with Susan Murphy, Ph.D.)}\\%  \hfill June 2016--June 2017\\
%\textit{Advisor: Susan Murphy, Ph.D.}\\
Performed data management and statistical analysis for the results of a micro-randomized trial of HeartSteps, an mHealth intervention to increase  physical activity among cardiac rehabilitation patients. Developed a time-varying standardized effect size for the micro-randomized trial design. 

}

{\bf The University of Wisconsin-Madison}, Madison, WI\\
Project Assistant \hfill Spring 2015

{\addtolength{\leftskip}{15pt}
 Created realistic data sets and example research problems for a new Master's-level
  statistical methods and data analysis course.

}

{\bf Epic Systems Corporation}, Verona, WI\\
Business Intelligence Developer \hfill July 2012--June 2013

{\addtolength{\leftskip}{15pt}
 Developed reporting content and utilities for hospital
  admissions data using Intersystems
  Cach\'{e}, SQL, and Crystal Reports.
 Supported Epic customers and
  staff using Epic reporting tools.

}

\begin{absolutelynopagebreak}
{\bf American Institues for Research}, Washington, D.C.\\
Research Assistant \hfill Summer 2011

{\addtolength{\leftskip}{15pt}
    Supported staff at the National Center for Education Statistics
   working on the Integrated Postsecondary Education Data System
   (IPEDS).
 Developed web tutorials for the IPEDS data collection
   system.
 Fulfilled data requests in SAS using IPEDS data.


}

\end{absolutelynopagebreak}

\section{PUBLICATIONS}

\textbf{Luers, B.}, Qian, M., Nahum-Shani, I., Kasari, C. Almirall, D. (2019). Linear mixed models for comparing dynamic treatment regimens on a longitudinal outcome in sequentially randomized trials. \href{https://arxiv.org/abs/1910.10078}{(preprint)}

\textbf{Luers, B.}, Klasnja, P., and Murphy, S.A. (2018). Standardized effect sizes for preventive mobile health interventions in micro-randomized trials. \textit{Prevention Science}. \href{https://doi.org/10.1007/s11121-017-0862-5}{(link)}

Klasnja, P., Smith, S., Seewald, N.J., Lee, A., Hall, K., \textbf{Luers, B.}, Hekler, E.B. and Murphy, S.A. (2018). Effectiveness of contextually tailored suggestions for physical activity: A micro-randomized optimization trial of HeartSteps. \textit{Annals of Behavioral Medicine}. \href{https://doi.org/10.1093/abm/kay067}{(link)}

\section{PRESENTATIONS}

\textbf{Luers, B.} Mixed effects models for sequential, multiple assignment randomized trials (SMARTs).
Joint Statistical Meetings, Denver, CO. July 2019. (poster)

\textbf{Luers, B.} Power and tuning for the knockoff filter. 
Michigan Student Symposium for Interdisciplinary Statistical Science,
Ann Arbor, MI. March 2019. (poster)

\textbf{Luers, B.}, Qian, M., Nahum-Shani, I., Kasari, C., and Almirall, D. 
Mixed effect models to compare dynamic treatment regimens with SMART data. 
ENAR Spring Meeting, Philadelphia, PA. March 2019. (presentation)

\textbf{Luers, B.} Dimension reduction and binary discrimination for naturalistic driving studies with heterogeneity. 
Michigan Student Symposium for Interdisciplinary Statistical Sciences, Ann Arbor, MI. April 2018. (poster)

\textbf{Luers, B.} and Shedden, K. Fingerprinting individual driving behavior with vehicle kinematics data and dimension reduction regression. Michigan Institute for Data Science Annual Symposium, Ann Arbor, MI. October 2017. (poster)

NeCamp, T., Yoo, H., \textbf{Luers, B.}, Cho, A., Seewald, N., Klasnja, P., and Murphy, S.A. HeartSteps: A Case Study in Trial Design and Evaluation of Mobile Health Interventions. Michigan Institute for Data Science Annual Symposium, Ann Arbor, MI. November 2016. (poster)
%Timothy NeCamp, Hyesun Yoo, Brook Luers, April Cho, Nick Seewald, Predrag Klasnja, Susan Murphy


\section{TEACHING EXPERIENCE}
{\bf University of Michigan}, Ann Arbor, MI \\
Department of Statistics

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}%STATS 415
Data Mining and Statistical Learning \hfill Fall 2019, Winter 2020

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}%STATS 306,
Introduction to Statistical Computing \hfill Fall 2017

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}%STATS 412, 
Introduction to Probability and Statistics \hfill Winter 2016

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}%STATS 250,
Introduction to Statistics and Data Analysis \hfill Fall 2015

\vspace{6pt}
\begin{absolutelynopagebreak}
{\bf University of Wisconsin-Madison}, Madison, WI\\
Department of Statistics
\end{absolutelynopagebreak}

\hspace{15pt}Instructor\\
\hspace{15pt}%STAT 301, 
Introduction to Statistical Methods \hfill Fall 2014

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}%STAT 301, 
Introduction to Statistical Methods\hfill Spring 2014

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}%STAT 224, 
Introductory Statistics for Engineers \hfill Fall 2013

\vspace{6pt}
{\bf Summer Institute for Training in Biostatistics}, Madison, WI\\
University of Wisconsin-Madison

\hspace{15pt}Teaching Assistant\\
\hspace{15pt}Introduction to Biostatistics, Biostatistics Practicum\hfill Summer 2014

\vspace{6pt}
{\bf Oberlin College}, Oberlin OH\\
Department of Mathematics

\hspace{15pt}Calculus Tutor \hfill Fall 2009--Spring 2010, Spring 2011

\hspace{15pt}Statistics Grader\hfill Spring 2012
%{\bf Mathematics Grader}  \hfill Feb.--May 2012\\
%Oberlin College, Oberlin, OH
%\begin{itemize}
% %\item Graded weekly homework assignments for an introductory statistics
%   course.
% \end{itemize}

\vspace{18pt}
\section{HONORS AND AWARDS}          
Honorable Mention, Outstanding Graduate Student Instructor, University of Michigan (Spring 2016)

Member, Phi Beta Kappa Society (May 2012)

Junior Fellow, Joint Program in Survey Methodology (Summer 2011)
   
\section{SKILLS}
Statistical modeling and inference

Data analysis and visualization

R, Python, Go, Stan, tidyverse, scipy, SQL, C++, Intersystems Cach\'{e}

\label{sec:lastpage}
\end{document}
